---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Systematic Analysis of Lens-Expressed RNA-Binding Proteins"
```

# CveklRBP2019

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/paullangard/CveklRBP2019/master?urlpath=rstudio)

This repository contains the data and code for our paper:

> Paul Langard, Ales Cvekl (2019). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

Our pre-print is online here:

> Paul Langard, Ales Cvekl (2019). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>


### How to cite

Please cite this compendium as:

> Paul Langard, Ales Cvekl, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to download or install

You can download the compendium as a zip from from this URL: <https://github.com/paullangard/CveklRBP2019/archive/master.zip>

Or you can install this compendium as an R package, CveklRBP2019, from GitHub with:


```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("paullangard/CveklRBP2019")
```


### Licenses

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code :** See the [DESCRIPTION](DESCRIPTION) file



