---
title: "Census RBP"
author: "Paul Langard"
date: "23 décembre 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(magrittr)
library(CveklRBP2019)
require(biomaRt)
```

The post-transcriptional regulation network is not extensively studied in the lens. With this aim in mind, we wanted to study RNA-binding proteins functions that are expressed in the lens. 

The first step of this analysis is to make a list of RNA-binding proteins, and filter for lens-expression.

# Make a list of RNA-binding proteins

So as to produce a list of RNA-binding proteins, we can use published census such as Gerstberger et al. (2014), the RBP database, the functional annotations of our proteomic dataset and concatenate those. 

## Census from RBPDB

```{r censusRBPDB, cache=T}
t_CensusRBPDB <- read_tsv("../../data/raw_data/RBPCensus/CensusRBPDB2012.tsv", col_names = c("genename"), col_types = "____c") %>% 
  drop_na() %>% 
  distinct() %>%
  mutate(genename=sapply(genename, simpleCap)) %>%
  #from alias2Symbol, if a Symbol is available, otherwise return the initial genename
  mutate(genename=unlist(sapply(genename, alias2Symbol_Cvekl))) %>% 
  distinct() %$% genename
```

## RNA-binding annotated proteins from Zhao proteomic dataset

```{r censusZhao, cache=T}
t_CensusZhao2018 <- t_proteomicZhao2018 %>% 
  filter_all(any_vars(str_detect(., pattern = "RNA-binding"))) %>%
  filter(!GeneNames %in% c('Tsn','Impdh2','Nudt5','Tdrkh','Trir','Jmjd6','Ro60', "Trove2"))%>%
  arrange(GeneNames) %$% GeneNames
```

```{r}
t_proteomicZhao2018_RBP <- t_proteomicZhao2018 %>%
  dplyr::filter(gene %in% c(t_CensusRBPDB, t_CensusZhao2018)) %>%
  filter_at(vars(rankEpith, rankFibers), any_vars(.<=1800)) %>%
  dplyr::filter(!str_detect(gene, "Gm|D1Pas1")) %>%
  mutate(PWMavailable = case_when(gene %in% t_CensusRBPDB ~ T,
                                   T ~ F)) %>%
  mutate(tissue = case_when(rankFibers <= 1800 & rankEpith > 1800 ~ "fibers",
                            rankEpith <= 1800 & rankFibers > 1800 ~ "epi",
                            rankEpith <= 1800 & rankFibers <= 1800 ~ "both"))

t_proteomicZhao2018_RBP %>% write_rds("../../data/derived_data/t_proteomicZhao2018_RBP.rds")
```


<!-- ## Census from Huang 2018 -->

<!-- ```{r censusHuang, eval=F, include=F} -->
<!-- t_CensusHuang2018 <- readxl::read_xlsx("CensusRBPHuang2018_PNAS.xlsx", sheet="DS1.Mass Data", skip=1)  %>% drop_na() %>% -->
<!--   dplyr::select(proteinname=`Protein name`, genename=Gene, Classification) %>% -->
<!--   separate_rows(genename, sep=";") %>% -->
<!--     #use MGI symbol convention, first letter is a major caps, the rest is lower -->
<!--   mutate(genename=sapply(genename, simpleCap)) %>% -->
<!--   #from alias2Symbol, if a Symbol is available, otherwise return the initial genename -->
<!--   mutate(genename=unlist(sapply(genename, alias2Symbol_Cvekl)))  -->
<!-- ``` -->


<!-- ## Census from Nature -->

<!-- ```{r censusNature, eval=F, include=F} -->
<!-- t_CensusGerstberger2014 <-readxl::read_xls(path="CensusRBPGerstberger2014_Nature.xls",sheet="RBP table")  %>% -->
<!--   rename(genename=`gene name`) %>% -->
<!--   #use MGI symbol convention, first letter is a major caps, the rest is lower -->
<!--   mutate(genename=sapply(genename, simpleCap)) %>% -->
<!--   #from alias2Symbol, if a Symbol is available, otherwise return the initial genename -->
<!--   mutate(genename=unlist(sapply(genename, alias2Symbol_Cvekl)))  -->

<!-- ``` -->

<!-- Then we gather everything together, and filter for expression within our proteomic dataset.  -->



